---
title: "Data Mining Chapter 12 Homework"
author: "Pooria Assarehha"
date: "2024-01-26"
output: pdf_document
---

# Discovering knowledge in Data Chapter 12

```{r, message=FALSE}
df = read.csv("table12-8.csv", stringsAsFactors = TRUE)
library(arules)
```

```{r}
rules <- apriori(df[-1])
inspect(sort(rules))
```

## Ex 12.4


| $F_1$     | Count |
| --------- | ----- | 
| Sunny     | 5     | 
| Overcast  | 4     | 
| Rain      | 5     | 
| Hot       | 4     | 
| Mild      | 7     | 
| Cool      | 4     | 
| High      | 7     | 
| Normal    | 7     | 
| Windy:True| 6     | 
| Windy:False| 8     | 
| Play:Yes  | 9      |
| Play:No    | 5     |

## Ex 12.5


2-itemsets: $F_1 \times F_1$

| 2-itemsets            | Count | 2-itemsets            | Count | 2-itemsets            | Count | 2-itemsets                | Count |
| ------------------    | ----- | ----------------------| ----- | -------------------   | ----- | -----------------------   | ----- |
|HumNormal, NonWindy    | 4     |   PlayNo, PlayYes     |   ,   |   PlayNo, Cool        |   ,   |     HumHigh, Rain         |    ,  |
|NonWindy,PlayYes       | 6     |   Rain, PlayNo        |   ,   |   PlayYes, Mild       |   ,   |     HumHigh, Mild         |    ,  |
|Rain, NonWindy         | 3     |   NonWindy, Sunny     |   ,   |   Rain, Mild          |   ,   |     HumHigh, NonWindy     |    ,  |
|Overcast, PlayNo       | 0     |   PlayNo, Windy       |   ,   |   HumNormal, PlayNo   |   ,   |     Hot, NonWindy         |    ,  |
|HumNormal, Cool        |       |   Mild, Windy         |   ,   |   HumHigh, Sunny      |   ,   |     Overcast, Mild        |    ,  |
|PlayYes, Overcast      |       |   Overcast, NonWindy  |   ,   |   Overcast, Windy     |   ,   |     Hot, Sunny            |    ,  |
|Rain, PlayYes          |,      |   HumNormal, Mild     |   ,   |   Cool, Overcast      |   ,   |     PlayYes, Sunny        |    ,  |
|HumHigh, PlayNo        |,      |   Windy, Sunny        |   ,   |   HumNormal, Hot      |   ,   |     Rain, Sunny           |    ,  |
|PlayNo, Sunny          |,      |   Cool, Sunny         |   ,   |   Hot, Windy          |   ,   |     HumNormal, Windy      |    ,  |
|Cool, NonWindy         |,      |   HumNormal, PlayYes  |   ,   |   PlayYes, Windy      |   ,   |     HumHigh, Overcast     |    ,  |
|Mild, Sunny            |,      |   HumNormal, Rain     |   ,   |   Rain, Windy         |   ,   |     Hot, Overcast         |    ,  |
|PlayNo, NonWindy       |,      |   PlayYes, Hot        |   ,   |   Cool, PlayYes       |   ,   |     Mild, NonWindy        |    ,  |
|Cool, Windy            |,      |   HumHigh, Windy      |   ,   |   HumNormal, Sunny    |   ,   |     HumNormal, Overcast   |    ,  |
|HumHigh, Hot           |,      |   Rain, Hot           |   ,   |   Rain, Cool          |   ,   |     PlayNo, Hot           |    ,  |
|HumHigh, PlayYes       |,      |   HumHigh, Cool       |   ,   |   PlayNo, Mild        |   ,   |                           |       |


## Ex 12.6
## Ex 12.7
## Ex 12.8
## Ex 12.9
## Ex 12.11

# Hands-on Analysis
