---
title: "Assarehha-610300080-HW2"
author: "Pooria Assarehha"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Chapter 2 Exercises 

## Ex 7

The missing data could have a pattern and omitting them may create bias.

## Ex 9

It preserves the mean and variance, but it may create data that does not exist.

## Ex 24

75 is the outlier.

```{r}
stock.price.data = c(10,7,20 ,12,75, 15, 9, 18, 4, 12, 8, 14)
mu = mean(stock.price.data)
Z = (stock.price.data - mu)/sd(stock.price.data)
stock.price.data[Z>3 | Z< -3]
```

```{r}
Q1 = quantile(stock.price.data, 0.25)
Q3 = quantile(stock.price.data, 0.75)
iqr = IQR(stock.price.data)
stock.price.data[(stock.price.data > (Q3 + 1.5*iqr)) | (stock.price.data < (Q1 - 1.5*iqr))]
```

## Ex 26

```{r}
print(paste0("with the outlier -> mean: ", 
mean(stock.price.data), " median: ",
median(stock.price.data)))
print(paste0("without outlier -> mean: ",
mean(stock.price.data[!(Z>3 | Z< -3)]), " median: ",
median(stock.price.data[!(Z>3 | Z< -3)])))
```
the median is unchaged after ommiting the outlier. but the mean is reduced by ~30%.

## Ex 28 
```{r}
dada = c(1,1,1,3,3,7)
width = 3
binned = list("1-4" =c(1,1,1,3), "4-7" = c() , "7-10" = c(7))
binned
```
## Ex 29

(1,1) , (1,3) , (3,7)

## Ex 30

the first has unbalanced bin population, the second does not segregate values.


## Ex 33
```{r}
churn <- read.csv(file="../churn.csv", stringsAsFactors = FALSE)
sum(is.na(churn), axis=0)
```
No missing value?

## Ex 34
```{r}
unique(churn$State)
unique(churn$Area.Code)
```
## Ex 35
```{r}
plot(churn$CustServ.Calls)
```

## Ex 36

```{r}
calls = churn$CustServ.Calls
Z.calls = (calls - mean(calls))/sd(calls)
calls[Z.calls > 3 | Z.calls < -3]
c(-3, 3)*sd(calls) + mean(calls)
```
```{r}
q1 = quantile(calls, 0.25)
q3 = quantile(calls, 0.75)
iqr = IQR(calls)

c(q1 - 1.5*iqr, q3+1.5*iqr)
```

## Ex 37 
```{r}
daymin = churn$Day.Mins 
daymin = (daymin - mean(daymin))/sd(daymin)
head(daymin)
```
## Ex 38
```{r}
skw <- function(data){3*(mean(data) - median(data))/sd(data)}
skw(churn$Day.Mins)
skw(daymin)
```
Z transformation preserves skewness.
It's nearly symmetric.

## Ex 39
```{r}
m = mean(churn$Day.Mins)
s = sd(churn$Day.Mins)
hist(churn$Day.Mins)

qqnorm(churn$Day.Mins, col="red", datax = TRUE)
qqline(churn$Day.Mins, col="blue", datax=TRUE)
```
Symmetric deviation in the end edges?

## Ex 40
```{r}
hist(churn$Intl.Mins)
qqnorm(churn$Night.Mins, col="red",
       datax = TRUE,
       main = "Normal Q-Q Plot of Z-Transform of Int Mins")
qqline(churn$Night.Mins, col="blue", datax=TRUE)

churn$Zero.Intl = churn$Intl.Mins == 0
nonzerointlmin = churn$Intl.Mins[!churn$Zero.Intl]
hist(nonzerointlmin)
qqnorm(nonzerointlmin, col="red")
qqline(nonzerointlmin)
```

we can see a little improvement.

## Ex 41

```{r}
nmins = churn$Night.Mins
zscore <- function(data){(data - mean(data))/sd(data)}
z.nmins = zscore(nmins)
boxplot(z.nmins, horizontal = TRUE, xaxp=c(min(z.nmins),max(z.nmins), 4))

```


