---
title: "Data Mining Chapter 10 HW"
author: "Pooria Assarehha"
date: "2024-01-19"
output: pdf_document
---

# Discovering Knowledge in Data Chapter 10

## Ex 10.4

at each Step, we calculate the distance of each 2 data points. Distance is simply the difference. at each step we merge those with minimum distance for any of members of 2 clusters. 

Step 0, each record is a cluster, those with zero distance become one cluster.

Step 1, distance between 1 and 0s is 1. 9 and 10s is 1. they will merge.

Step 2, d(3,1) = 2, d(7,9) = 2 => merge

Step 3, d(3,6) = 3 => merge

```{r, message=FALSE}
library(cluster)
dat = c(0,0,1,3,3,6,7,9,10,10)
names(dat) <- dat
dend = as.dendrogram(agnes(dat, method = "single"))
plot(
  dend,
  xlab="Data points",
  ylab="Steps",
  main = "Single-Linkage Clustering"
)
```

## Ex 10.6

```{r}
data = matrix(
  c(2,0,1,2,2,2,3,2,2,3,3,3,2,4,3,4,4,4,3,5),
  byrow = TRUE,
  ncol = 2
  )
colnames(data)<- c("x","y")
rownames(data) <- c("a", "B", "c", "d", "e", "f", "g", "h", "i", "j")
plot(data, xlab="x", ylab="y", main="Data Points")
```

$$
$$

```{r}
kmeans(data, 2)
```

## Ex 10.7



# Hands-on Analysis

## Ex 10.12

```{r}
rm(list=ls())
setwd("~/Documents/Amar 1400 UT/4021_Fall 2023/Data Mining/Assignment")
dat <- read.csv("../cereals.csv", stringsAsFactors = TRUE)
dat = dat[-c(1,16)]
str(dat)
```

```{r}
#km <- kmeans(dat, 5)
```

## Ex 10.13
