---
title: "Data Mining HW4"
author: "Pooria Assarehha"
date: "2023-12-10"
output: pdf_document
---

## Ex 4.10
margin of error is decreased either by decreasing $\alpha$ , which is not recommended
and by increasing number of samples (n). 

## Ex 4.14
p value can be interpreted as "the probability of finding a sample stronger than the current in rejecting H0". if its small then it is already strong. 

## Ex 4.17

$\alpha = 5 \Rightarrow Z_{1-\frac{\alpha}{2}} \approx 2$

```{r}
qnorm(0.975)
```

- n = 25 $20 \pm 2 \sqrt{\frac{5}{25}}$
- n = 100 $20 \pm 2 \sqrt{\frac{5}{100}}$
- n = 400 $20 \pm  2 \sqrt{\frac{5}{400}}$

## Ex 4.20

```{r}
p = 0.1; n = 1000
p + c(-1,1)*qnorm(0.95)*sqrt(p*(1-p)/n)
p + c(-1,1)*qnorm(0.975)*sqrt(p*(1-p)/n)
p + c(-1,1)*qnorm(0.995)*sqrt(p*(1-p)/n)

```

## Ex 4.23
```{r}
1 - pnorm((55 - 50)/(25/sqrt(100))) < qnorm(1 - 0.05)
```

if p-value is lower than $P(Z_{\alpha})$ then Reject $H_0: \mu > 50$ 

## Ex 4.26

$H_0: p < 0.25 \quad , \quad \alpha = 0.01$

```{r}
Zdata = (240/1000 - 0.25)/sqrt(0.24*(1-0.24)/1000)
if (Zdata < 0 ) pnorm(Zdata) < qnorm(1 - 0.01) else 1 - pnorm(Zdata) < qnorm(1 - 0.01)
pnorm(Zdata)
```
reject $H_0$
