---
title: "Data Mining HW5"
author: "Pooria Assarehha"
date: "2023-12-11"
output: pdf_document
---

## Ex 5.1
-- 2 sample t-test for difference in each part's proportion
-- Chi-2 homogen of fit
-- 2 sample t-test for difference in each part's mean

## Ex 5.2
$H_0: \bar{x}_1 - \bar{x}_2 = 0$

$$t_{data} = \frac{\bar{x}_1 - \bar{x}_2}{\sqrt{\frac{s^2_1}{n_1} + \frac{s^2_2}{n_2}}}$$

```{r}
tdata = (20.5 - 20.4)/sqrt(
  (5.2^2 / 2000) + (4.9^2 / 600)
)
2*pt(tdata, 2600-1) < qt(0.10/2, df=2600 -1)
```
do not reject $H_0$

## Ex 5.4
```{r}
trainp = c(800, 750, 450)
testp = c(240, 250, 110)

expect = (trainp / sum(trainp) )*sum(testp)
xi = sum((testp - expect)^2 / expect)

1 - pchisq(xi, df=2) < qchisq(0.10/2, df=2)
```
We reject $H_0$, test proportions are not homogen to train.

## Ex 5.6
(a) even with equal means, variances effect how evident the sample is to reject or not reject the null hyp.

(b) 
- between : variability in sample means
- within : variability in each group

(c) $S^2$, variance or standard deviation

(d) when $S_b$ >> $S_w$ , Reject $H_0$ : equal means

## Ex 5.7

```{r}
credit = c(100, 110, 90, 100)
debit = c(80, 120, 90, 110)
check = c(50, 70, 80, 80)

means = sapply(list(credit, debit, check), mean)
s_w = sapply(list(credit, debit, check), sd)
s_b = sum(sapply(means, length)*(means - mean(means))^2)/(length(means)-1)
s_w
s_b
```

## Ex 5.10


# Hands-on Analysis

## Ex 5.11
## Ex 5.13
## Ex 5.15
## Ex 5.16
## Ex 5.17
## Ex 5.18
## Ex 5.19
## Ex 5.20
## Ex 5.21
## Ex 5.22
## Ex 5.23


